M.Sc. Proposal: \\ \bigskip Computational Electrokinetics

### 2010-09-27 notes/proposal.tex
Fix proposal.

\title{M.Sc. Proposal}
\author{Roman Zeyde \\ \\  {\small Advisor: Prof. Irad Yavneh} }
\begin{document}
\maketitle
\section{Introduction}
Electrokinetic theory describes the dynamics of charged particles
in ionic fluids. When a particle acquires surface charge, a layer
of ions of opposite charge is attracted to the surface via
electric forces, creating a double-layer structure around the
particle (see Figure \ref{fig:EDL}). This structure, called
``Debye layer'', electrically screens the surface charge, thus
creating a potential difference between the particle and the outer
layer of the fluid bulk.
\begin{figure}[htbp]
\begin{framed}
    \begin{center}
        \includegraphics[width=0.25\textwidth]
            {ElectricDoubleLayer.eps}
        \caption{Schematic structure of the double layer:
        (1) particle surface, (2) Debye layer and (3) fluid bulk.
        If the particle surface has positive (blue) surface charge,
        it attracts negative (red) ions from the fluid making the
        Debye layer negatively charged (as opposed to the rest of
        the fluid bulk, which is electrically neutral).
        Zeta potential is defined as the voltage drop on (2).}
        \label{fig:EDL}
    \end{center}
\end{framed}
\end{figure}
In cases where the layer width is much smaller than the particle's
size, an analytical asymptotic solution for the Debye layer
dynamics can be found \cite{Yariv10a}.

Electrokinetics is described by the following physical phenomena (in dimensionless formulation):
\begin{enumerate}
\item Electrostatics---the fluid bulk contains no free
charge:
\begin{equation} \label{eq:Laplace}
    \bnabla \cdot (C \bnabla \varPhi) = 0 \, .
\end{equation}
\item Fluid dynamics---Stokes flow with an electrostatic force
component:
\begin{equation} \label{eq:Stokes}
\left\{ \begin{array}{l}
\bLaplacian \bV - \bnabla P + \Laplacian \varPhi \bnabla \varPhi = 0 \, , \\
\bnabla \cdot \bV = 0 \, . \end{array} \right.
\end{equation}
\item Ion diffusion and advection (via the fluid's velocity field):
\begin{equation} \label{eq:Nernst}
\Laplacian C - \alpha \bV \cdot \bnabla C = 0 \, .
\end{equation}
\end{enumerate}
The variables of the electrokinetic problem are the electrostatic 
potential $\varPhi$, fluid's velocity $\bV$ and its pressure $P$ 
and ionic concentration $C$.

>>>>

\title{M.Sc. Proposal: \\ \bigskip
Computational Electrokinetics}
\author{Roman Zeyde \\ \\  {\small Advisor: Prof. Irad Yavneh} }
\begin{document}
\maketitle
\section{Introduction}
Electrokinetic theory describes the dynamics of charged particles
in ionic fluids. When a particle acquires surface charge, a layer
of ions of opposite charge is attracted to the surface via
electric forces, creating a double-layer structure around the
particle (see Figure \ref{fig:EDL}). This structure, called
``Debye layer'', electrically screens the surface charge, thus
creating a potential difference between the particle and the outer
layer of the fluid bulk.
\begin{figure}[htbp]
\begin{framed}
    \begin{center}
        \includegraphics[width=0.25\textwidth]
            {ElectricDoubleLayer.eps}
        \caption{Schematic structure of the double layer:
        (1) particle surface, (2) Debye layer and (3) fluid bulk.
        If the particle surface has positive (blue) surface charge,
        it attracts negative (red) ions from the fluid making the
        Debye layer negatively charged (as opposed to the rest of
        the fluid bulk, which is electrically neutral).
        Zeta potential is defined as the voltage drop on (2).}
        \label{fig:EDL}
    \end{center}
\end{framed}
\end{figure}
In cases where the layer width is much smaller than the particle's
size, an analytical asymptotic solution for the Debye layer
dynamics can be found \cite{Yariv10a}.

Electrokinetics is described by the following physical phenomena (in dimensionless formulation):
\begin{enumerate}
\item Electrostatics---the fluid bulk contains no free
charge:
\begin{equation} \label{eq:Laplace}
    \bnabla \cdot (C \bnabla \varPhi) = 0 \, .
\end{equation}
\item Fluid dynamics---Stokes flow with an electrostatic force
component:
\begin{equation} \label{eq:Stokes}
\left\{ \begin{array}{l}
\bLaplacian \bV - \bnabla P + \Laplacian \varPhi \bnabla \varPhi = 0 \, , \\
\bnabla \cdot \bV = 0 \, . \end{array} \right.
\end{equation}
\item Ion diffusion and advection (via the fluid's velocity field):
\begin{equation} \label{eq:Nernst}
\Laplacian C - \alpha \bV \cdot \bnabla C = 0 \, .
\end{equation}
\end{enumerate}
The variables of the electrokinetic problem are the electrostatic
potential $\varPhi$, fluid velocity $\bV$ and its pressure $P$ and
ionic concentration $C$.
